How to Write Theses\\ With Two Line Titles

### 2020-04-22 chapters/litReview/finalLit.tex
Final final

\section{Testing without oracle}
Testing is one of the most crucial activities in the software development life cycle. Bertolino \cite{Bertolino2007} define software testing as, \enquote{observing the execution of a software system to validate whether it behaves as intended and identify potential malfunctions}. Software testing is a very common practice in the software industry and is used to ensure the quality of the product. Software testing is an umbrella term that encompasses a wide range of different sub tasks, like unit testing a small piece of code, acceptance testing a large information system for customer validation, monitoring the application at run-time to ensure continuous service, etc.\cite{Bertolino2007} A study by Beizer \cite{Beizer1990} has estimated that software testing can use up to fifty percent, or more, of the total development cost. Thus, it is clear that program software testing is worthy of our attention for research and improvement \cite{Beizer1990}.\\
Weyuker \cite{Weyuker} categorizes the testing research activities into three categories:
\begin{enumerate}
  \item \enquote{Develop a sound theoretical basis for testing}.
  \item \enquote{Devise and improve testing methodologies, especially the mechanizable ones}.
  \item \enquote{Define accurate measurement criteria for testing data adequately}.
\end{enumerate}

@@

 A third and more effective method of addressing some of the concerns about the oracle problem is the use of differential testing. McKeeman \cite{McKeeman98differentialtesting} first introduced the idea of differential testing, which works by testing a dataset on two or more comparable systems. The systems are run with mechanically generated test cases, and their output is observed. If one of the systems crashes or goes into an infinite loop, we have detected a potential bug in the implementation. Differential testing is widely used as a method to discover semantic bugs. It has successfully uncovered bugs in various domains like C compilers, JVM, SSL/TLS implementations, etc. However, since it requires two or more similar systems, it inherits some of the same problems of pseudo-oracle testing. Developing sophisticated oracles is another way of encountering the oracle problem. If the oracles are very relaxed such that they tolerate the effects of uncertainties, then there is a chance that a fault may be masked. On the other hand, f the oracles are too narrow, it may cause them to generate false positives, resulting in wasted developer's time \cite{Elbaum2014}.

>>>>

\section{Testing without oracle}
Testing is one of the most crucial activities in the software development life cycle. Bertolino \cite{Bertolino2007} define software testing as, \enquote{observing the execution of a software system to validate whether it behaves as intended and identify potential malfunctions}. Software testing is a very common practice in the software industry and is used to ensure the quality of the product. Software testing is an umbrella term that encompasses a wide range of different sub tasks, like unit testing a small piece of code, acceptance testing a large information system for customer validation, monitoring the application at run-time to ensure continuous service, etc \cite{Bertolino2007}. A study by Beizer \cite{Beizer1990} has estimated that software testing can use up to fifty percent, or more, of the total development cost. Thus, it is clear that program software testing is worthy of our attention for research and improvement \cite{Beizer1990}.\\
Weyuker \cite{Weyuker} categorizes the testing research activities into three categories:
\begin{enumerate}
  \item \enquote{Develop a sound theoretical basis for testing}.
  \item \enquote{Devise and improve testing methodologies, especially the mechanizable ones}.
  \item \enquote{Define accurate measurement criteria for testing data adequately}.
\end{enumerate}

@@

 A third and more effective method of addressing some of the concerns about the oracle problem is by the use of differential testing. Differential testing focuses on two main objectives; one is that the behaviors that are supposed to remain unchanged do so, and the second is that all the discrepancies in the output are explained. McKeeman \cite{McKeeman98differentialtesting} first introduced the idea of differential testing, which works by testing a dataset on multiple comparable systems. In differential testing, two versions of a software system are selected. One bug-free version of the program is chosen while the other is a test version, which is a modified version of the program and, thus, needs testing. The systems are run with mechanically generated test cases, and their output is observed. If one of the systems crashes or goes into an infinite loop, we have detected a potential bug in the implementation. Differential testing is widely used as a method to discover semantic bugs. It has successfully uncovered bugs in various domains like C compilers, JVM, SSL/TLS implementations, etc. Gulzar, Zhu, and Han \cite{gulzar2019} conducted a log analysis of 2104 diff tests from an organization-wide diff testing framework at Google and found that the main reason behind the popularity of diff tests is their ability to simulate real production systems and their low maintenance overhead. However, since it requires two or more similar systems, it inherits some of the same problems of pseudo-oracle testing. They also identified some other limitations of differential testing, where they are found to be more time-intensive to run and often generate noisy and flaky outcomes \cite{gulzar2019}.

 Developing sophisticated oracles is another way of encountering the oracle problem. If the oracles are very relaxed such that they tolerate the effects of uncertainties, then there is a chance that a fault may be masked. On the other hand, f the oracles are too narrow, it may cause them to generate false positives, resulting in wasted developer's time \cite{Elbaum2014}.

### 2020-04-22 chapters/methodology/dataset.tex
Final final

\subsection{EMNIST Dataset}
% The EMNIST dataset is a set of handwritten character digits derived from the NIST Special Database 19
% and converted to a 28x28 pixel image format. 
The EMNIST dataset has the same shape as MNIST dataset. They are 28x28 pixels of handwritten characters that are derived from the "NIST Special Database 19". There are six different splits provided in this dataset. The splits are organized by class, by balance, by type, etc. Some splits are unbalanced and contain an uneven number of examples for classes. The EMNIST-Digit and EMNIST-MNIST datasets are directly compatible with the original MNIST dataset. For this study, we choose "EMNIST Letters" split, which has $145,600$ characters in 26 balanced classes where each class has the same number of samples. The characters are in uppercase and lowercase, which have have been merged into one 26-class set.
The figure \ref{fig:emnist-letter} shows a sample image of the EMNIST-Letter dataset.

@@

\subsection{Fashion MNIST Dataset}
Zalando's article images consist of a set of $55,000$ training examples and $10,000$ test examples. The dataset is commonly referred to as the Fashion-MNIST dataset. Every data point in the dataset is a grayscale image of size 28x28. The labels in the dataset have a value between $[0, 9]$. Table \ref{tbl:MNIST-Fashion} shows a sample of the dataset.

>>>>

\subsection{EMNIST Dataset}
% The EMNIST dataset is a set of handwritten character digits derived from the NIST Special Database 19
% and converted to a 28x28 pixel image format. 
The EMNIST dataset has the same shape as MNIST dataset. They are 28x28 pixels of handwritten characters that are derived from the "NIST Special Database 19". There are six different splits provided in this dataset. The splits are organized by class, by balance, by type, etc. Some splits are unbalanced and contain an uneven number of examples for classes. The EMNIST-Digit and EMNIST-MNIST datasets are directly compatible with the original MNIST dataset. For this study, we choose "EMNIST Letters" split, which has $119,800$ characters in 26 balanced classes where each class has the same number of samples. The characters are in uppercase and lowercase, which have have been merged into one 26-class set.
The figure \ref{fig:emnist-letter} shows a sample image of the EMNIST-Letter dataset.

@@

\subsection{Fashion MNIST Dataset}
A dataset of Zalando's article images which consist of a set of $55,000$ training examples and $10,000$ test examples. The dataset is commonly referred to as the Fashion-MNIST dataset. Every data point in the dataset is a grayscale image of size 28x28. The labels in the dataset have a value between $[0, 9]$. Table \ref{tbl:MNIST-Fashion} shows a sample of the dataset.

### 2020-04-22 chapters/methodology/properties.tex
Final final

\section{Identifying Metamorphic Relations} \label{identifyingMR}
To answer our first research question, we implemented some affine transformations on the datasets as possible candidates for metamorphic properties. We observed that applying these affine transformations on the dataset to a very small degree produced similar accuracy as that of the original dataset. Thus we selected these five transformations as metamorphic properties for each dataset: rotate, shear, shade, shift the image along $x$-axis, and shift the image along $y$-axis. Each image in the testing dataset (MNIST, Fashion-MNIST, and EMNIST-Letter) was transformed using these five metamorphic properties. We used Keras image preprocessing functions to apply these transformations to the test data in each dataset to generate new data to measure robustness.

@@

\subsection{Shade}
We represent the pixels of the MNIST images as floating point numbers between 0 and 1 where 0 is white, and 1 represents black. To apply the shade transformation, we increased the non-black pixels by $0.01$ for every image until they became black.
    \begin{figure}[htb!]
        \centering
        \begin{subfigure}[b]{.3\textwidth}
            \centering
            \includegraphics[width=\linewidth]{images/shade1.png}
            \caption{Value: 0}
            \label{fig:Rotate-misclass0}
        \end{subfigure}%
        \begin{subfigure}[b]{.3\textwidth}
            \centering
            \includegraphics[width=\textwidth]{images/shade2.png}
            \caption{Value: 80}
            \label{fig:Rotate-misclass0}
        \end{subfigure}%
        \begin{subfigure}[b]{.3\textwidth}
            \centering
            \includegraphics[width=\linewidth]{images/shade3.png}
            \caption{Value: 99}
            \label{fig:Rotate-misclass0}
        \end{subfigure}

@@

\subsection{Shift the image along the X axis(ShiftX)}
Since the images are $28$ pixels wide, shifting the images by more than 28 pixels in either direction moved the images out of the frame completely. Thus, we transformed the test datasets by moving each image by pixels between 0 and 28 in both the X directions. We used ImageDataGenerator's $apply\_transform()$ function with $tx$ parameter and a pixel value in order to perform this transformation. This generated 56 follow-up test dataset of the original data where each version differs from the last by $1$ pixel shift along the $x$ axis.
    \begin{figure}[htb!]
        \centering
        \begin{subfigure}[b]{.3\textwidth}
            \centering
            \includegraphics[width=\linewidth]{images/shiftx1.png}
            \caption{Value: 10}
            \label{fig:Rotate-misclass0}
        \end{subfigure}%
        \begin{subfigure}[b]{.3\textwidth}
            \centering
            \includegraphics[width=\textwidth]{images/shiftx2.png}
            \caption{Value: 0}
            \label{fig:Rotate-misclass0}
        \end{subfigure}%
        \begin{subfigure}[b]{.3\textwidth}
            \centering
            \includegraphics[width=\linewidth]{images/shiftx3.png}
            \caption{Value: -10}
            \label{fig:Rotate-misclass0}
        \end{subfigure}

@@

\subsection{Shift the image along the Y axis(ShiftY)}
The last metamorphic property we identified was shifting the images on the Y-axis. We used ImageDataGenerator's $apply\_transform()$ function with $ty$ parameter to transform the test data. Since the images are 28x28 pixels, we shifted the images by each pixel between 0 and 28 pixels in both Y directions. 
    \begin{figure}[htb!]
        \centering
        \begin{subfigure}[b]{.3\textwidth}
            \centering
            \includegraphics[width=\linewidth]{images/shifty1.png}
            \caption{Value: -10}
            \label{fig:Rotate-misclass0}
        \end{subfigure}%
        \begin{subfigure}[b]{.3\textwidth}
            \centering
            \includegraphics[width=\textwidth]{images/shifty2.png}
            \caption{Value: 0}
            \label{fig:Rotate-misclass0}
        \end{subfigure}%
        \begin{subfigure}[b]{.3\textwidth}
            \centering
            \includegraphics[width=\linewidth]{images/shifty3.png}
            \caption{Value: 10}
            \label{fig:Rotate-misclass0}
        \end{subfigure}

>>>>

\section{Identifying Metamorphic Transformations} \label{identifyingMR}
Some common problems with images are that they can have some small random rotations, or they could be located a bit off from the center, or the exposure of the picture could be high. These problems with images prompted us to look into affine transformations as a possible set of transformations to use for this project. To answer our first research question, we implemented some affine transformations on the datasets as possible candidates for metamorphic properties. We observed that applying these affine transformations on the dataset to a very small degree produced similar accuracy as that of the original dataset. Thus we selected these five transformations as metamorphic properties for each dataset: rotate, shear, shade, shift the image along $x$-axis, and shift the image along $y$-axis. It should be noted that there more affine transformations than the five we identified, and they can be used as metamorphic transformation as well. However, these transformations appear to be the most common ways one can manipulate image datasets. Each image in the testing dataset (MNIST, Fashion-MNIST, and EMNIST-Letter) was transformed using these five metamorphic properties. We used Keras image preprocessing functions to apply these transformations to the test data in each dataset to generate new data to measure robustness.

After some primary investigation using the transformed datasets and some standard machine learning algorithms, we saw that the machine learning algorithms produced very similar accuracies on datasets, which were very similar to the original dataset. Thus, we defined our metamorphic relation as "a small change in the input from a known test case should lead to a similarly small change (or no change) in the output." We use this metamorphic relation for all the transformations.

@@

\subsection{Shade}
We represent the pixels of the MNIST images as floating point numbers between 0 and 1 where 0 is white, and 1 represents black. To apply the shade transformation, we increased the non-black pixels by $0.01$ for every image until they became black.
    \begin{figure}[htb!]
        \centering
        \begin{subfigure}[b]{.3\textwidth}
            \centering
            \includegraphics[width=\linewidth]{images/shade1.png}
            \caption{Shading Value: 0}
            \label{fig:Rotate-misclass0}
        \end{subfigure}%
        \begin{subfigure}[b]{.3\textwidth}
            \centering
            \includegraphics[width=\textwidth]{images/shade2.png}
            \caption{Shading Value: 0.80}
            \label{fig:Rotate-misclass0}
        \end{subfigure}%
        \begin{subfigure}[b]{.3\textwidth}
            \centering
            \includegraphics[width=\linewidth]{images/shade3.png}
            \caption{Shading Value: 0. 99}
            \label{fig:Rotate-misclass0}
        \end{subfigure}

@@

\subsection{Shift the image along the X axis(ShiftX)}
Since the images are $28$ pixels wide, shifting the images by more than 28 pixels in either direction moved the images out of the frame completely. Thus, we transformed the test datasets by moving each image by pixels between 0 and 28 in both the X directions. We used ImageDataGenerator's $apply\_transform()$ function with $tx$ parameter and a pixel value in order to perform this transformation. This generated 56 follow-up test dataset of the original data where each version differs from the last by $1$ pixel shift along the $x$ axis.
    \begin{figure}[htb!]
        \centering
        \begin{subfigure}[b]{.3\textwidth}
            \centering
            \includegraphics[width=\linewidth]{images/shiftx1.png}
            \caption{Pixel shift: 10}
            \label{fig:Rotate-misclass0}
        \end{subfigure}%
        \begin{subfigure}[b]{.3\textwidth}
            \centering
            \includegraphics[width=\textwidth]{images/shiftx2.png}
            \caption{Pixel shift: 0}
            \label{fig:Rotate-misclass0}
        \end{subfigure}%
        \begin{subfigure}[b]{.3\textwidth}
            \centering
            \includegraphics[width=\linewidth]{images/shiftx3.png}
            \caption{Pixel shift: -10}
            \label{fig:Rotate-misclass0}
        \end{subfigure}

@@

\subsection{Shift the image along the Y axis(ShiftY)}
The last metamorphic property we identified was shifting the images on the Y-axis. We used ImageDataGenerator's $apply\_transform()$ function with $ty$ parameter to transform the test data. Since the images are 28x28 pixels, we shifted the images by each pixel between 0 and 28 pixels in both Y directions. 
    \begin{figure}[htb!]
        \centering
        \begin{subfigure}[b]{.3\textwidth}
            \centering
            \includegraphics[width=\linewidth]{images/shifty1.png}
            \caption{Pixel shift: -10}
            \label{fig:Rotate-misclass0}
        \end{subfigure}%
        \begin{subfigure}[b]{.3\textwidth}
            \centering
            \includegraphics[width=\textwidth]{images/shifty2.png}
            \caption{Pixel shift: 0}
            \label{fig:Rotate-misclass0}
        \end{subfigure}%
        \begin{subfigure}[b]{.3\textwidth}
            \centering
            \includegraphics[width=\linewidth]{images/shifty3.png}
            \caption{Pixel shift: 10}
            \label{fig:Rotate-misclass0}
        \end{subfigure}

### 2020-04-22 chapters/results/BackupOfRobustnessData.tex
Final final

\begin{groupplot}[group style={group size= 1 by 2},xtick=\empty]%[ybar stacked,xtick=\empty,]%ytick=\empty]
\nextgroupplot[ylabel={Degree of transfromation},ybar, bar width=.2cm,xtick=\empty,yshift=1cm, ymin=0,ymax=100,legend style = {at={(1.05, 0.5)}, anchor = west, legend columns =1, draw=none, area legend},  ymajorgrids = true,width=0.85\textwidth,height=.5\textwidth,]%ytick=\empty]
\addplot[fill=blue,draw=black] table[x=RotateX,y=RotateY]{\mnistx};
\addplot[fill=red,draw=black] table[x=ShadeX,y=ShadeY]{\mnistx};
\addplot[fill=green,draw=black] table[x=ShearX,y=ShearY]{\mnistx};
\addplot[fill=yellow,draw=black] table[x=ShiftXX,y=ShiftXY]{\mnistx};
\addplot[fill=brown,draw=black] table[x=ShiftYX,y=ShiftYY]{\mnistx};

@@

\nextgroupplot[ybar, width=0.85\textwidth,height=.5\textwidth, bar width=.2cm,yshift=1cm,ymin=-100,ymax=0,legend style = {at={(1.05, 1.65)}, anchor = west, legend columns =1, draw=none, area    legend},ymajorgrids = true,xtick=data, xticklabels from table={\mnisty}{Algo}, xticklabel style={yshift=-2ex, xshift=-2ex,anchor= west},xlabel={Algorithms}]
\addplot[fill=blue,draw=black] table[x=RotateX,y=RotateY]{\mnisty};
\addplot[fill=red,draw=black] table[x=ShadeX,y=ShadeY]{\mnisty};
\addplot[fill=green,draw=black] table[x=ShearX,y=ShearY]{\mnisty};
\addplot[fill=yellow,draw=black] table[x=ShiftXX,y=ShiftXY]{\mnisty};
\addplot[fill=brown,draw=black] table[x=ShiftYX,y=ShiftYY]{\mnisty};

@@

The figure \ref{fig:RobGraphforFashion} shows the same graph for the Fahion-MNIST dataset. Here the Naive Bayes algorithm shows the most robustness for all the five transformations since the dataset can be transformed for larger values before the accuracy is dissimilar to the original dataset.

@@

Similarly, for the MNIST-Letter dataset, we find that the $k$NN algorithm is the most robust for all the transformation except shading. For the shading algorithm, the Naive Bayes algorithm shows the most robustness.

>>>>

\begin{groupplot}[group style={group size= 1 by 2},xtick=\empty]%[ybar stacked,xtick=\empty,]%ytick=\empty]
\nextgroupplot[ylabel={Degree of transfromation},ybar, bar width=.2cm,xtick=\empty,yshift=1cm, ymin=0,ymax=100,legend style = {at={(1.05, 0.5)}, anchor = west, legend columns =1, draw=none, area legend},  ymajorgrids = true,width=0.85\textwidth,height=.4\textwidth,]%ytick=\empty]
\addplot[fill=blue,draw=black] table[x=RotateX,y=RotateY]{\mnistx};
\addplot[fill=red,draw=black] table[x=ShadeX,y=ShadeY]{\mnistx};
\addplot[fill=green,draw=black] table[x=ShearX,y=ShearY]{\mnistx};
\addplot[fill=yellow,draw=black] table[x=ShiftXX,y=ShiftXY]{\mnistx};
\addplot[fill=brown,draw=black] table[x=ShiftYX,y=ShiftYY]{\mnistx};

@@

\nextgroupplot[ybar, width=0.85\textwidth,height=.4\textwidth, bar width=.2cm,yshift=1cm,ymin=-100,ymax=0,legend style = {at={(1.05, 1.65)}, anchor = west, legend columns =1, draw=none, area    legend},ymajorgrids = true,xtick=data, xticklabels from table={\mnisty}{Algo}, xticklabel style={yshift=-2ex, xshift=-2ex,anchor= west},xlabel={Algorithms}]
\addplot[fill=blue,draw=black] table[x=RotateX,y=RotateY]{\mnisty};
\addplot[fill=red,draw=black] table[x=ShadeX,y=ShadeY]{\mnisty};
\addplot[fill=green,draw=black] table[x=ShearX,y=ShearY]{\mnisty};
\addplot[fill=yellow,draw=black] table[x=ShiftXX,y=ShiftXY]{\mnisty};
\addplot[fill=brown,draw=black] table[x=ShiftYX,y=ShiftYY]{\mnisty};

@@

The figure \ref{fig:RobGraphforFashion} shows the same graph for the Fahion-MNIST dataset. Here the Naive Bayes algorithm shows the most robustness for all the five transformations since the dataset can be transformed for larger values before the accuracy drops significantly lower than the original dataset.

@@

Similarly, for the MNIST-Letter dataset, we find that the $k$NN algorithm is the most robust for all the transformation except shading. For the shading algorithm, the Naive Bayes algorithm once again shows the most robustness.

### 2020-04-22 chapters/results/discussion.tex
Final final

\section{Conclusion}
In this study, we set to investigate three main questions: can we identify new metamorphic properties to be used with image datasets? Do these properties affect all the classes equally? And what range of transformation can be applied, such that the follow-up test data remains similar to original data? We answered the first question by naming five affine transformations, which can be used as metamorphic properties. We also implemented them on three datasets to generate new test cases. To answer the second research question, we implemented five machine learning algorithms and tested the accuracy of the new test cases for each class. We found that the classes had different areas under curve for metamorphic transformations; thus, they are affected differently by the different metamorphic transformations. 
We also made recommendations to select parameters for our metamorphic transformations such that the resulting follow-up test cases are similar to the original dataset. These recommendations can be used as a test case generation strategy to generate additional transformed test data for MNIST, Fashion-MNIST, and EMNIST-Letter dataset. Future researches should consider using our metamorphic transformations and recommendations to generate new test cases for machine learning algorithms.

>>>>

\section{Conclusion}
In this study, we set to investigate three main questions: can we identify new metamorphic properties to be used with image datasets? Do these properties affect all the classes equally? And what range of transformation can be applied, such that the follow-up test data remains similar to original data? We answered the first question by naming five affine transformations, which can be used as metamorphic properties. We also implemented them on three datasets to generate new test cases. To answer the second research question, we implemented five machine learning algorithms and tested the accuracy of the new test cases for each class. We found that the classes had different areas under curve for metamorphic transformations; thus, they are affected differently by the different metamorphic transformations. 
We also made recommendations to select parameters for our metamorphic transformations such that the resulting follow-up test cases are similar to the original dataset. These recommendations can be used as a test case generation strategy to generate additional transformed test data for MNIST, Fashion-MNIST, and EMNIST-Letter dataset. Future researches should consider using our metamorphic transformations and recommendations to generate new test cases for their machine learning algorithms.
